Accelerated Magnetic Resonance Imaging by Adversarial Neural Network

### 2018-02-05 paper.tex
update

%--------------------- METHOD --------------------%
\section{Method}\label{method_section}

\subsection{K-space}
Let $\bm{u}$ denote the desired signal, a 2D MR image, obtained by the IFFT of the complex k-space signal $s_{0}$. Let $M_{F}$ denote a full sampling mask such that the reconstructed MR image is: 
\begin{equation}
\bm{u}=F^{H}M_{F}\odot s_{0}
\end{equation} 
where $H$ is the Hermitian transpose operation, $\odot$ denotes element-wise multiplication, and $F^{H}$ is an orthonormal 2D IFFT operator, such that $F^{H}F=I$. 
While sampling part of the k-space, using $M_{p}$ as a sampling mask, the reconstructed MR image suffers from artifacts and aliasing. An example artifacts caused by under-sampling and zero padding in the phase axis using a Gaussian mask (40\%) is shown in Figure \textbf{\ref{fig:pair_of_k_space_mri}}.

@@

		} & \subfloat[\textcolor{black}{\scriptsize{}fully sampled MRI}]{\centering{}\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/example_original.png}

@@

		} & \subfloat[\textcolor{black}{\scriptsize{}Zero-filled}]{\centering{}\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/example_zeroPadding.png}
}\tabularnewline
\end{tabular}\caption{\textcolor{black}{\footnotesize{}{}Under-sampling artifacts: the
	arrows illustrate the sampling methodology}}
\label{fig:pair_of_k_space_mri} 
\end{figure}

\subsection{Objective}

Let $s_{p}=M_{p}\odot s_{0}$ denote the under-sampled k-space. Given a sampling mask and a model $f$, defined by the set of parameters $\Theta$, our goal is to estimate the missing k-space samples such that: 
\begin{equation}
\Theta=\arg\min_{\Theta}L(F^{H}f\left(s_{p};\Theta\right),\boldsymbol{u})
\end{equation}
where $L\left(\cdot\right)$ is the loss function. While choosing the loss to be L2 norm is reasonable for natural images, for the k-space, which has different spatial features, this may not be enough. As mentioned in \cite{pathak2016context}, L2 minimization provides a blurry solution, results in a loss of fine details. 
Averaging the high frequency details in the k-space domain results in very poor reconstruction. In order to address this problem, we used the adversarial loss, based on GAN.

We trained our model using the adversarial strategy, as described in \cite{goodfellow2014generative,radford2015unsupervised}. 
This method is based on a generator $G$, which takes noise \textbf{$z$ }with uniform distribution \textbf{$p_{u}\left(z\right)$} as input and generates samples from the data distribution. A discriminator $D$ is trained to distinguish between ``real'' examples from the data and generated (``fake'') examples from $G.$ During the training process, we optimize $G$ to maximize the discriminator's probability of error. Simultaneously, $D$ is getting better and provides more
accurate predictions.

Let $s_{0}$ denote a ``real'' k-space sample from the distribution $p_{r}\left(s_{0}\right)$. The following optimization process can be described by two-players min-max game:

\begin{equation}
\min_{G}\max_{D}\mathbb{E_{\mathrm{s_{0}\sim p_{r}\left(s_{0}\right)}}\mathrm{\log\left[D\left(x\right)\right]}}+\mathbb{E_{\mathrm{z\sim p_{u}\left(z\right)}}\mathrm{\log\left[1-D\left(G(z)\right)\right]}}
\end{equation}

@@

\subsection{Network Architecture}

>>>>

%--------------------- METHOD --------------------%
\section{Method}\label{method_section}
We aim to address MRI reconstruction from under-sampled k-space data using DNN. We hereby present the proposed methodology as well as the network architecture.
\subsection{Notations and Problem Definition}
Let $\bm{u}$ denote the desired signal, a 2D MR image, obtained by IFFT of the complex k-space signal $s_{0}$ i.e, 
\begin{equation}
\bm{u}=F^{H}s_{0}
\end{equation} 
where $H$ is the Hermitian transpose operation and $F^{H}$ is an orthonormal 2D IFFT operator, such that $F^{H}F=I$. 
Partial k-space sampling, results in MR images that are subject to artifacts and aliasing. 
Figure~\textbf{\ref{fig:pair_of_k_space_mri}}.d exemplifies artifacts caused by under-sampling and zero padding in the phase axis using a Gaussian mask (40\%).

@@

		} & \subfloat[\textcolor{black}{\scriptsize{}original }]{\centering{}\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/example_original.png}

@@

		} & \subfloat[\textcolor{black}{\scriptsize{}reconstructed}]{\centering{}\includegraphics[width=2.5cm,height=2.5cm]{include/grp2/example_zeroPadding.png}
}\tabularnewline
\end{tabular}\caption{\textcolor{black}{\footnotesize{}{}Under-sampling artifacts: the
	arrows illustrate Cartesian sampling}}
\label{fig:pair_of_k_space_mri} 
\end{figure}

Let $s_{p}=M_{p}\odot s_{0}$ denote the under-sampled k-space, where $\odot$ denotes element-wise multiplication and $M_{p}$ is the sampling mask. Given a model $f$, defined by the set of parameters $\Theta$, our goal is to estimate the missing k-space samples such that: 
\begin{equation}
\Theta=\arg\min_{\Theta}L(F^{H}f\left(s_{p};\Theta\right),\boldsymbol{u})
\end{equation}
where $L\left(\cdot\right)$ is a loss function. L2 loss is widely used for natural image reconstruction. However, as mentioned in \cite{pathak2016context}, L2 minimization provides a blurry solution, results in a loss of fine details. In our case, where spatial frequencies in the form of k-space are considered, using this loss alone may be inappropriate, resulting in poor reconstruction. To address this problem, we proposed using in addition an adversarial loss, based on GAN.

\subsection{K-space GAN}
We train our model using an adversarial strategy, as described in \cite{goodfellow2014generative,radford2015unsupervised}. 
This method is based on a generator $G$, which gets noise \textbf{$z$ }with uniform distribution \textbf{$p_{u}\left(z\right)$} as input and generates samples from the observed data distribution. A discriminator $D$ is trained to distinguish between ``true'' examples from the data and generated (``fake'') examples from $G.$ During the training process, we optimize $G$ to maximize the discriminator's probability of error. Simultaneously, $D$ is enhanced and provides more accurate predictions.

Let $s_{0}$ denote a true k-space sample from the distribution $p_{r}\left(s_{0}\right)$. The following optimization process can be described by two-players min-max value function $V(G,D)$:

\begin{equation}
\min_{G}\max_{D}V(G,D) = \mathbb{E_{\mathrm{s_{0}\sim p_{r}\left(s_{0}\right)}}\mathrm{\log\left[D\left(x\right)\right]}}+\mathbb{E_{\mathrm{z\sim p_{u}\left(z\right)}}\mathrm{\log\left[1-D\left(G(z)\right)\right]}}
\end{equation}

@@

\subsection{System Architecture}
